### 2024-02-20 paper_sisc_first_revision/localpsf.tex
paper down to 32 pages. hooray!
fix comma typo

The idea of the proposed method, which we refer to throughout the paper as the ``PSF-based method'', is to use \emph{impulse response interpolation} to form a high rank approximation of $\Aop$ using a small number of operator applications. The impulse response, $\phi_x$, associated with a point, $x$, is the Riesz representation\footnote{Recall that the Riesz representative of a functional $\rho \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\rho^* \in L^2(\Omega)$ such that $\rho(w) = \left(\rho^*,w\right)_{L^2(\Omega)}$ for all $w \in L^2(\Omega)$.} of the linear functional that results from applying $\Aop$ to a delta distribution (i.e., point source, impulse) centered at $x$. We compute batches of impulse responses by applying $\Aop$ to weighted sums of delta distributions associated with batches of points scattered throughout the domain (see Figure~\ref{fig:batches_intro}). Batches of impulse responses may be thought of intuitively as sets of ``columns'' of the kernel (Figure \ref{fig:frog_kernel_impulse_responses}). To choose the batches, we form ellipsoid estimates for the supports of all $\phi_x$ via a moment method (Figure~\ref{fig:frog_moments_ellipsoid}) that involves applying $\Aop^T$ to a small number of polynomials (see Section~\ref{sec:intromoments}). We then use a greedy ellipsoid packing algorithm (Figure~\ref{fig:frog_batches}) to maximize the number of impulse responses per batch.
% which requires us to estimate the supports of the impulse responses $\phi_x$ \emph{before} they are computed. 
Then we interpolate translated and scaled versions of these impulse responses to approximate entries of the operator's integral kernel (Figure~\ref{fig:hmatrix_neighbors_frog}). Adding more batches yields impulse responses at more points, increasing the approximation accuracy at the cost of one operator application per batch (Figure~\ref{fig:frog_column_errors}).

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.2]{frog_hmatrix_knn_impulse3.pdf}	
	\caption{Left: H-matrix structure for $\Aker$. Computing an entry of this matrix requires evaluating the integral kernel, $\Phi(y,x)$, at a pair of points $(y,x) \in \Omega \times \Omega$.  Center: Kernel evaluation points $x$ and $y$ (black circles),  sample points for the approximation (light gray and black dots), and the $k_n$ sample points, $x'$, that are nearest to $x$ (black dots). Right: Known impulse response at $x'$. Using radial basis function interpolation, the desired kernel entry is approximated as a weighted linear combination of translated and scaled versions of impulse responses at the points $x'$ (Section~\ref{sec:approximate_kernel_entries}).
%		the values $\phi_{x’}(y - \spatialmean(x) + \spatialmean(x’))$ for these nearby points $x'$.
%	Right:  Illustration of the radial basis function interpolation method used to approximate $\Aker(y,x)$ by a weighted linear combination of the values $\frac{\spatialvol(x)}{\spatialvol(x’)}\phi_{x’}(y - \spatialmean(x) + \spatialmean(x’))$ for a small number of sample points near $x$. The weights are determined by radial basis function (RBF) interpolation. Right: The impulse response centered at $x’$.
	}
	\label{fig:hmatrix_neighbors_frog}
\end{figure}

>>>>

The idea of the proposed method, which we refer to throughout the paper as the ``PSF-based method,'' is to use \emph{impulse response interpolation} to form a high rank approximation of $\Aop$ using a small number of operator applications. The impulse response, $\phi_x$, associated with a point, $x$, is the Riesz representation\footnote{Recall that the Riesz representative of a functional $\rho \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\rho^* \in L^2(\Omega)$ such that $\rho(w) = \left(\rho^*,w\right)_{L^2(\Omega)}$ for all $w \in L^2(\Omega)$.} of the linear functional that results from applying $\Aop$ to a delta distribution (i.e., point source, impulse) centered at $x$. We compute batches of impulse responses by applying $\Aop$ to weighted sums of delta distributions associated with batches of points scattered throughout the domain (see Figure~\ref{fig:batches_intro}). Batches of impulse responses may be thought of intuitively as sets of ``columns'' of the kernel (Figure \ref{fig:frog_kernel_impulse_responses}). To choose the batches, we form ellipsoid estimates for the supports of all $\phi_x$ via a moment method (Figure~\ref{fig:frog_moments_ellipsoid}) that involves applying $\Aop^T$ to a small number of polynomials (see Section~\ref{sec:intromoments}). We then use a greedy ellipsoid packing algorithm (Figure~\ref{fig:frog_batches}) to maximize the number of impulse responses per batch.
% which requires us to estimate the supports of the impulse responses $\phi_x$ \emph{before} they are computed. 
Then we interpolate translated and scaled versions of these impulse responses to approximate entries of the operator's integral kernel (Figure~\ref{fig:hmatrix_neighbors_frog}). Adding more batches yields impulse responses at more points, increasing the approximation accuracy at the cost of one operator application per batch (Figure~\ref{fig:frog_column_errors}).

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.18]{frog_hmatrix_knn_impulse3.pdf}	
	\caption{Left: H-matrix structure for $\Aker$. Computing an entry of this matrix requires evaluating the integral kernel, $\Phi(y,x)$, at a pair of points $(y,x) \in \Omega \times \Omega$.  Center: Kernel evaluation points $x$ and $y$ (black circles),  sample points for the approximation (light gray and black dots), and the $k_n$ sample points, $x'$, that are nearest to $x$ (black dots). Right: Known impulse response at $x'$. Using radial basis function interpolation, the desired kernel entry is approximated as a weighted linear combination of translated and scaled versions of impulse responses at the points $x'$ (Section~\ref{sec:approximate_kernel_entries}).
%		the values $\phi_{x’}(y - \spatialmean(x) + \spatialmean(x’))$ for these nearby points $x'$.
%	Right:  Illustration of the radial basis function interpolation method used to approximate $\Aker(y,x)$ by a weighted linear combination of the values $\frac{\spatialvol(x)}{\spatialvol(x’)}\phi_{x’}(y - \spatialmean(x) + \spatialmean(x’))$ for a small number of sample points near $x$. The weights are determined by radial basis function (RBF) interpolation. Right: The impulse response centered at $x’$.
	}
	\label{fig:hmatrix_neighbors_frog}
\end{figure}
